% BangorEE - (an unofficial) Electronic Engineering Dissertation LaTeX Class.
% Usage info and bug reports at https://github.com/owenjones/bangoree

\documentclass[msc]{bangoree}

\usepackage{lipsum} % To create some filler content
\usepackage[style=authoryear-ibid]{biblatex}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{appendix}

\title{Leksis, an Adaptive Vocabulary Test For Low-Resource Languages}
\author{Alan Kersaudy}
\course{Language Technologies}
\date{September, 2025}
\supervisor{Dr. G. Bovolenta}

\addbibresource{references.bib}


\begin{document}
    \renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
    \renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}}
    \renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}.\arabic{enumiv}}
    \maketitle
    \statements
    \include{chapters/0_abstract}
    \acknowledgements{
      Any quality that may be found in this dissertation should not be attribued to its autor, who only bears the small responsability of puting together ideas, insights, and reflections from others. Even this small effort was itself directly or indirectly supported by people and institutions who made my stay in Bangor as pleasant, beneficial and productive as it could possibly have been. Especially, I owe a direct debt to Giulia Bovolenta, who first oriented me towards vocabulary testing, and whose many insights guided each steps through this work. Maria Kolesnichenko is the lighthouse of kind common sense that kept me from drowning in a sea of bad ideas during the whole year. Melanie Jouitteau, who first seeded in my mind the idea of doing this Master degree in Bangor. The teaching of Philip Davies in the TSI course who helped me improve my Welsh skills, along with fellow Welsh speaking students that I can only be gratefull to call friends, Leena Farhat, Tom Williams, Stephen Russel and Owen Williams. Preben Vanberg among many things is the person responsible for the idea of placing the items difficulty on the same logistic scale as the test takers. The whole team of the Canolfan Bedwyr, among which Tegau, Cat, Alun, Steffano and many others. But especially its Technology Unit's director Gruffydd Prys and his family, whose effort in welcoming me and supporting my stay in Bangor cannot be given justice with words. Two other teachers, Dewi Bryn Jones and Bill Teahan, who, in a very different but complementary way, helped me to master many of the skills that made this work possible. Finally, the financial support I was given from Cymen is an opportunity that motivated me to produce the best tool I could materially produce for the Welsh language. I ultimately dedicate this test and the tutoring agent associated with it to Cymen and its directors Manon Cadwaladr and Aled Jones as well as Myfyr Prys, for their role in enabling the Cymen scholarship. Let it be small gesture of gratitude for the trust and freedom they've given me. I am blessed and grateful to have crossed the road of so many smart and good peoples and this work is mostly the fruit of their collective kindness.
    }
    \tables

    \content
    \include{chapters/1_introduction}

    \include{chapters/2_literature_review}

    \include{chapters/3_methodology}
    
    \include{chapters/4_results}

    \include{chapters/5_discussion}

    \begin{appendices}
      \include{chapters/annex}
    \end{appendices}

    \printbibliography
\end{document}
